\chapter*{Acknowledgments}

I have so many people to thank.

First of, thanks to the Haskell community, who have welcomed this
relative newcomer with open arms and minds. My first line of Haskell
was written only in 2011!

I am not one for large displays of school spirit. Nevertheless,
I cannot imagine a better place to get my doctorate than at Penn.
I will remain passionate in my advocacy for this graduate program
for many years to come.

The PLClub at Penn has been a constant source of camaraderie, help
on various subjects, and great talks. Thanks to Jianzhou, Mike, Chris,
Marco, Emilio, C\v{a}t\v{a}lin, Benoit, Benoit,
Vilhelm, Daniel, Bob, Justin, Arthur, Antal, Jennifer, Dmitri,
Leo, Robert, Kenny, Antoine, and Pedro.

Thanks to ``FC crew'' who put up with my last-minute reminders and
frequent rescheduling. David Darais, Iavor Diatchki,
 Andres L\"{o}h, Pedro Magalh\~{a}es, Conor McBride: thanks for all the great
discussions, and I look forward to many more to come.

Adam Gundry bulldozed the path for me. His dissertation was something of
a road-map for mine, and I always learn from his insight.

Sincere thanks to Peter-Michael Osera for leading the way toward
a position at a liberal arts college and for much humor, some of
it appropriate.

I owe a debt of gratitude to Brent Yorgey. He decided he was tired
of pursuing dependent types in Haskell just as I came along. He also
(co-)wrote a grant that was approved just in time to free up his
advisor to take on another student. Much of my success is due to
Brent's paving the way for me.

Dimitrios Vytiniotis was a welcoming co-host at Microsoft Research
when I was there. I still have scars from the many hours of battling the
proof dragon in his office.

None of this, quite literally, would be possible without the leap
of faith taken by Benjamin Pierce, to whom I argued for my acceptance
to Penn, over the phone, on a shared line in the middle of a campground
in the Caribbean, surrounded by children and families enjoying
their vacation. A condition of my acceptance was that I would not work
with Stephanie, who had no room for me, despite our matching interests.
I trust Benjamin does not regret this decision, even though I violated
this condition.

I offer a heartfelt thanks to Steve Zdancewic. From the beginning of my
time at Penn, I felt entirely at home knocking on his door at any
time to ask for advice or mentorship. I did not often take advantage of this,
but it was indeed a comfort knowing I could seek him out.

I cannot express enough gratitude toward my family, new and old,
who have supported me in
every way possible.

Simon Peyton Jones is a visionary leader for the Haskell community,
holding all of us together on the steady stride toward a more perfect
language. Simon's mentorship to me, personally, has been invaluable.
It is such an honor to work alongside you, Simon, and I look
forward to much collaboration to come.

Stephanie Weirich is the best advisor a student could ask for. She is
insightful, full of energy and ideas, and simply has an intuitive
grasp on how best to nudge me along. And she's brilliant. Stephanie,
thanks for pulling me out of your Haskell programming class five years
ago---that's what started us on this adventure. Somehow, you made me
feel right away that I was having interesting and novel ideas; in
retrospect, many of them were really yours, all along. This is
surely the sign of excellent academic advising.

I am left to thank my wife Amanda and daughter Emma. Both have been
with me every step of the way. Well, Emma missed some steps as she wasn't
walking for the first year or so, having been born two months before
I started at Penn. But tonight, she accurately summarized to Amanda
the difference between Dependent Haskell and Idris (one is a change
to an existing language while the other is a brand new one, but both
have dependent types). Children grow fast, and I know Emma is eager for
the day when I can finally explain to her what it is I do all day.

And for Amanda, these words will have to do, because no words can
truly express how I feel: I love you, and thank you.

\begin{flushright}
Richard A. Eisenberg\\
August 2016
\end{flushright}

%%  LocalWords:  PLClub Jianzhou Marco Emilio lin Benoit Vilhelm Antal FC
%%  LocalWords:  Darais Iavor Diatchki Andres Magalh Conor Gundry Osera Brent
%%  LocalWords:  Yorgey Brent's Dimitrios Vytiniotis Zdancewic Simon's Idris
%%  LocalWords:  Weirich
