\chapter{Introduction}

Haskell has become a wonderful and rich playground for type system
experimentation. Despite its relative longevity -- at 25 years
old~\cite{history-of-haskell} \rae{check!} -- type theorists still turn to
Haskell as a place to build new type system ideas and see how they work in a
practical setting~\cite{functional-dependencies, type-families, arrows, syb,
  closed-type-families, generics-with-closed-type-families, safe-coercions,
  pattern-match-and-gadts, helium-type-errors, etc}. As a result, Haskell's type system has grown
ever more intricate over the years. As the power of types in Haskell has
increased, Haskellers have started to integrate dependent types into their
programs~\cite{singletons, hasochism, she, clash, vinyl}, despite the fact
that today's Haskell\footnote{Throughout this dissertation, a reference to
  ``today's Haskell'' refers to the language implemented by the Glasgow
  Haskell Compiler (GHC), version 7.10, released in 2015.} does not internally
support dependent types. Indeed, the desire to program in Haskell but with
support for dependent types influenced the creation of Agda~\cite{agda} and
Idris~\cite{idris}; both are Haskell-like languages with support for full dependent
types.

This dissertation closes the gap, by adding support for dependent types into
Haskell directly. In this work, I detail both the changes to GHC's internal
language, known as System FC~\cite{system-fc}, and explain the changes to the
surface language necessary to support dependent types. Naturally, I must also
describe the elaboration from the surface language to the internal language,
including type inference. Along with the textual description contained in this
dissertation, I have also implemented support for dependent types in GHC directly;
I expect a future release of the software to include this support.

With an implementation of dependent types in Haskell available, I look forward
to seeing how the Haskell community builds on top of my work and discovers
more and more applications of dependent types.
