\begin{proposal}

\chapter{\color{proposal}Timeline}

Much of the work described in this proposal has already taken place:
\begin{enumerate}
\item The entirety of \pref{cha:system-fc} is simply collecting together previous
work on System FC.
\item Although some details have yet to be worked out (such as import/export lists
and the concrete syntax around promoting functions), much of the design of
Dependent Haskell has been worked out, as well.
\item The system described in previous work~\cite{nokinds} will form the
basis of System FCD.
\item I have an implementation\footnote{\url{https://github.com/goldfirere/ghc/},
the \texttt{nokinds} branch} available of GHC with merged types and kinds and
full kind equalities. This implementation successfully compiles itself and all
of GHC's standard libraries, as well as some examples testing the power of
kind equalities.
\end{enumerate}

Here are the major remaining tasks to complete:
\begin{enumerate}
\item System FCD will need to include dependent types
  This addition
  will be strongly influenced by the work of \citet{gundry-thesis}.
  There is some work to be done here, for sure, but no more than a solid
  month's worth, I estimate.
\item The surface language specification and type inference algorithm are
  already in draft form (though it is not in a state ready to share), with an
  attempt at a proof started. This area is surely the murkiest area of this
  dissertation. However, given the previous work in this area~\cite{gundry-thesis},
  I am confident that this will work out. I hope to finish the bulk of this work
  in a 2-month timeframe.
\item I need to finish polishing my existing implementation of kind equalities
  and merge with GHC's master branch. This will take 2 months, I estimate.
\item I need to implement $\Pi$ into GHC. I estimate this will take 3 months.
\item I will need to write up the dissertation. Given that some of this writing
  will happen concurrently with achieving the tasks above, I estimate this will
  take 1 further month.
\end{enumerate}

These estimates total to 9 months. Given that something is sure to fall behind,
and that I will take time off from this schedule to write a paper or two during
the next year, I think this is all reasonable to complete for late spring of 2016.

Here is a specific timeline of goals and dates:
\begin{enumerate}
\item Submit a POPL paper by July~10, 2015.
\item Merge current implementation of kind equalities by Sept.~15, 2015.
\item Write \pref{cha:fcd} and \pref{app:fc} by Oct.~15, 2015.
\item Implement $\Pi$ into GHC by Jan.~15, 2016. This implementation will
be functional, but perhaps unpolished.
\item Submit an ICFP paper by Mar.~1, 2016.
\item Write \pref{cha:type-inference} and \pref{app:inference} by May~1, 2016.
\item Write remaining parts of dissertation by June~1, 2016.
\item Defend dissertation by July~1, 2016.
\end{enumerate}

Note that I do \emph{not} expect to merge my implementation of Dependent
Haskell with GHC's master branch before defending the dissertation. While this
would be wonderful to achieve, I do not want to place all of the engineering
such a goal would entail on my critical path toward finishing the
dissertation. I expect to spend time during the summer of 2016 polishing the
implementation and hopefully to merge later in 2016.

\end{proposal}
