\chapter{Related work}
\label{cha:related}

\section{Comparison to \citet{gundry-thesis}}

\section{Comparison to Idris}

\begin{proposal}
Although I compare Dependent Haskell against Coq, Agda, and Idris throughout
this proposal, I plan on focusing on comparing just against Idris in this
section, as my work is closest to what has been done in Idris, and I think
this comparison will be the most illuminating.
\end{proposal}

\section{Comparison to Liquid Haskell}

\section{Applicability beyond Haskell}

\begin{proposal}
The knowledge gained in adding dependent types to Haskell will translate
to other environments as well. A key example will be the thought of adding
dependent types to a variant of ML. Going the other way, I will examine
adding more programmatic features to existing dependently typed languages
(in particular, Haskell's |newtype| construct).
\end{proposal}

\section{Future work}

\begin{proposal}
Though this dissertation will deliver |pi|, that's not the end of the story.
Here are some questions I have that I do not expect will be answered in the
course of writing this work.
\begin{itemize}
\item How to improve error messages? While my work will strive hard not to
degrade error messages for non-dependently-typed programs, I offer no
guarantee about the quality of error messages in programs with lots of
dependent types. How can these be improved? More generally, how can error
messages be customized by programmers to fit their domain?

\item What editor support is necessary to make dependent types in Haskell
practical?

\item Are there constructs that I have been unable to promote? How can these
be made to work in types?

\item How do we optimize a dependently typed program? Ideally, a program should
be optimized to the same level whether an argument is dependent or not. However,
optimizing |pi|-quantified arguments will amount to proving the optimizations
correct! How do we retain runtime performance in the face of dependent types?

\item How will dependent types interact with type-checker
  plugins~\cite{type-checker-plugins}? Can we use an SMT solver to make working
  with dependent types easier?

\item Dependent types will allow for proper dependent pairs ($\Sigma$-types).
  Is it worth introducing new syntax to support these useful constructs directly?
\end{itemize}
\end{proposal}
